paper2_resistance_mechanisms_mixtures

### 2016-06-02 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
starting single insecticide figs

```{r,echo=FALSE,results='hide'}
  library(resistance)
```

@@

*Before this add figures for effect of inputs on sole use.*
* contrasting pairs, or even 3 values, 0.1,0.5 & 0.9*
```{r, eval=TRUE, echo=FALSE, fig.height=4}

  #create empty object to hold input matrix for return
  #input <- NULL

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.2,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.2,
                      s.RR1_A0 = 0.2,
                      s.RR2_0B = 0.2 )

@@

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2)

@@

  plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  cat("Fig. a1. starting to look at single insecticide effects")
```

>>>>

```{r,echo=FALSE,results='hide'}
  library(resistance)
  library(ggplot2)
```

@@

* add figures for effect of inputs on sole use.*
* contrasting pairs, or even 3 values, 0.1,0.5 & 0.9*
```{r, eval=TRUE, echo=FALSE, fig.height=4}

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

@@

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.8, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

@@

  #plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  # now doing a better way
  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=h.RS1_A0)) + 
         #geom_line(aes(colour=h.RS1_A0)) )
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a1. Dominance effect on single insecticide.")

```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.5,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.8,
                      phi.SS2_0B = 0.5,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=h.RS1_A0)) + 
         #geom_line(aes(colour=h.RS1_A0)) )
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a2. Effectiveness effect on single insecticide.")

```
